---
title: Speed matching for each participant
output: 
  html_document:
    toc: true
    toc_depth: 5
---
```{r global, echo=FALSE, message=FALSE,results='hide'}
source('libsAndMore.R')
opts_chunk$set(echo=FALSE, fig.align='center', fig.height = 3.5)
```

```{r input, echo=FALSE, message=FALSE, results='hide'}
datSpeedMatchRaw <- readfiles(path = 'data', exp = 'SpeedMatch')
```

#### Number of trials 
```{r trials, message=FALSE}
datSpeedMatchRaw %>% group_by(subject, radius, speed, number) %>% 
  summarise(n=n())
```
Participants AD and MP collected a few less responses because they were not available more time. 

#### Checking outliers
```{r outlayers, message=FALSE}
plotOutlyersSpeed <- ggplot(datSpeedMatchRaw)+
  facet_grid(number ~ subject)+
  geom_abline(slope = 1, lty = 2)+
  geom_point(shape = 4, 
             aes(x = speed, y = response, color = factor(radius))) +
  scale_x_log10(breaks = 2^(1:5))+scale_y_log10(breaks = 2^(1:5)) +
  labs(x = p$speedLabel, y = p$speedMatchLabel)
plotOutlyersSpeed

outliers <- datSpeedMatchRaw %>% filter(response==60 | response==.1)
```
I remove `r length(outliers$response)` data points because they corresponded to keypresses without adjustment, that is, they corresponded to the initial values of the matching speed.  

```{r nooutlayers, message=FALSE}
datSpeedMatch <- setdiff(datSpeedMatchRaw, outliers)

plotNoOutlyersSpeed <- ggplot(datSpeedMatch)+
  facet_grid(number ~ subject)+
  geom_abline(slope = 1, lty = 2)+
  geom_point(shape = 4, 
             aes(x = speed, y = response, color = factor(radius))) +
  scale_x_log10(breaks = 2^(1:5))+scale_y_log10(breaks = 2^(1:5)) +
  labs(x = p$speedLabel, y = p$speedMatchLabel)
plotNoOutlyersSpeed
```

```{r averaging, message=FALSE}
speedMatch <- datSpeedMatch %>% 
  group_by(subject, radius, speed, number) %>% 
  do(bootstrappinggeom(., x = 'response', B = p$B, name = 'speedMatch')) 

speedMatch <- speedMatch %>% 
  mutate(freq = speed / (2 * pi * radius), tf = freq * number)
```

#### In terms of `r p$speedLabel` 
```{r plots, message=FALSE}
pSpeedMatchSpeedRadius <- ggplot(speedMatch, 
                 aes(x = speed, y = speedMatch, ymin = speedMatchMin, 
                     ymax = speedMatchMax, color = factor(radius)))+
  facet_grid(number ~ subject)+
  geom_abline(slope = 1, lty = 2)+
  geom_pointrange()+geom_line()+
  scale_x_log10(breaks = 2^(1:5))+scale_y_log10(breaks = 2^(1:5)) +
  labs(x = p$speedLabel, y = p$speedMatchLabel, color = p$radiusLabel)
pSpeedMatchSpeedRadius

pSpeedMatchSpeedNumber <- ggplot(speedMatch, 
                 aes(x = speed, y = speedMatch, ymin = speedMatchMin, 
                     ymax = speedMatchMax, color = factor(number)))+
  facet_grid(radius ~ subject)+
  geom_abline(slope = 1, lty = 2)+
  geom_pointrange()+geom_line()+
  scale_colour_manual(values = c(3,4)) +
  scale_x_log10(breaks = 2^(1:5))+scale_y_log10(breaks = 2^(1:5)) +
  labs(x = p$speedLabel, y = p$speedMatchLabel)
pSpeedMatchSpeedNumber
```

#### Plotting the differences in terms of `r p$speedLabel` 
```{r plotFreqDif, message=FALSE}
speedMatchFig <- speedMatch
speedMatchFig$speed[speedMatchFig$radius==4] <- 
  speedMatchFig$speed[speedMatchFig$radius==4] * 1.08

speedMatchFig$numberFig <- speedMatchFig$number
speedMatchFig$numberFig <- factor(speedMatchFig$numberFig,
                      levels = c(1, 2),
                      labels = c(p$oneObjectLabel, p$twoObjectsLabel))

speedMatchFig$radiusFig <- speedMatchFig$radius
speedMatchFig$radiusFig <- factor(speedMatchFig$radiusFig,
                      levels = c(2, 4),
                      labels = c(p$smallRadiusLabel, p$largeRadiusLabel))

speedMatchFig$subjectFig <- paste('Observer',speedMatchFig$subject)

pSpeedMatchSpeedRadiusDif <- ggplot(speedMatchFig, 
                 aes(x = speed, y = (speedMatch) / speed, 
                     ymin = (speedMatchMin) / speed, 
                     ymax = (speedMatchMax) /speed, 
                     color = factor(radiusFig),
                     shape = factor(radiusFig)))+
  facet_grid(numberFig ~ subjectFig)+
  geom_hline(yintercept = 1, lty = 2,size = p$sizeLine)+
  geom_point(size = p$sizePointSpeed)+geom_line(size = p$sizeLine)+
  geom_linerange(size = p$sizeLine, width=.04)+
  scale_x_log10(breaks = 2^(1:5))+
  labs(x = p$speedLabel, y = p$normalizedSpeedLabel, color = p$radiusLabel,
        shape = p$radiusLabel)+
  theme(panel.grid=element_blank(),
        legend.key = element_blank())
pSpeedMatchSpeedRadiusDif


speedMatchFigNumber <- speedMatch
speedMatchFigNumber$speed[speedMatchFigNumber$number==2] <- 
  speedMatchFigNumber$speed[speedMatchFigNumber$number==2] * 1.08

speedMatchFigNumber$numberFig <- speedMatchFigNumber$number
speedMatchFigNumber$numberFig <- factor(speedMatchFigNumber$numberFig,
                      levels = c(1, 2),
                      labels = c(p$oneObjectLabel, p$twoObjectsLabel))

speedMatchFigNumber$radiusFig <- speedMatchFigNumber$radius
speedMatchFigNumber$radiusFig <- factor(speedMatchFigNumber$radiusFig,
                      levels = c(2, 4),
                      labels = c(p$smallRadiusLabel, p$largeRadiusLabel))

speedMatchFigNumber$subjectFig <- paste('Observer',speedMatchFigNumber$subject)

pSpeedMatchSpeedNumberDif <- ggplot(speedMatchFigNumber, 
                 aes(x = speed, y = (speedMatch) / speed, 
                     ymin = (speedMatchMin) / speed, 
                     ymax = (speedMatchMax) /speed, 
                     color = factor(numberFig),
                     shape = factor(numberFig)))+
  facet_grid(radiusFig ~ subjectFig)+
  geom_hline(yintercept = 1, lty = 2,size = p$sizeLine)+
  geom_point(size = p$sizePointSpeed)+geom_line(size = p$sizeLine)+
  geom_linerange(size = p$sizeLine, width=.04)+
  scale_color_manual(values = c(3,4)) +
  scale_x_log10(breaks = 2^(1:5))+
  labs(x = p$speedLabel, y = p$normalizedSpeedLabel, color = p$numberLabel,
        shape = p$numberLabel)+
  theme(panel.grid=element_blank(),
        legend.key = element_blank())

pSpeedMatchSpeedNumberDif



```

```{r output}
write.table(speedMatch,'logdata/speedMatch.txt')
```
