---
title: Frequency matching for each participant
output: 
  html_document:
    toc: true
    toc_depth: 5
---

```{r global, echo=FALSE,message=FALSE,results='hide'}
source('libsAndMore.R')
opts_chunk$set(echo=FALSE, fig.align='center', fig.height = 3.5)
```

```{r input, echo=FALSE, message=FALSE, results='hide'}
datFreqMatchRaw <- readfiles(path = 'data', exp = 'FreqMatch')
```

#### Number of trials
```{r numberTrials, message=FALSE}
datFreqMatchRaw %>% group_by(subject, radius, speed, number) %>% 
  summarise(n=n())
```

#### Checking outliers
```{r outlayers, message=FALSE}
plotOutliers <- ggplot(datFreqMatchRaw)+
  facet_grid(number ~ subject)+
  geom_abline(slope = 1, lty = 2)+
  geom_point(shape = 4, 
             aes(x = speed, y = response, color = factor(radius))) +
  scale_x_log10(breaks = 2^(1:5))+scale_y_log10(breaks = 2^(1:5)) +
  labs(x = p$speedLabel, y = p$speedMatchLabel)
plotOutliers

outlier1 <- datFreqMatchRaw %>% 
  filter(subject == 'SY', number == 1, response == max(response) )

outlier2 <- datFreqMatchRaw %>% 
  filter(subject == 'SY', number == 2, response == min(response) )
```
For participant SY, the reported speed for `r outlier1$speed` was `r outlier1$response` and the reported speed for `r outlier2$speed` was `r outlier2$response`. These are two clear outlyers. Probably the participant pressed the button to adjust involuntarily. I removed those points. 

```{r nooutlayers, message=FALSE}
datFreqMatch <- setdiff(datFreqMatchRaw, outlier1)
datFreqMatch <- setdiff(datFreqMatch, outlier2)

plotNoOutliers <- ggplot(datFreqMatch)+
  facet_grid(number ~ subject)+
  geom_abline(slope = 1, lty = 2)+
  geom_point(shape = 4, 
             aes(x = speed, y = response, color = factor(radius))) +
  scale_x_log10(breaks = 2^(1:5))+scale_y_log10(breaks = 2^(1:5)) +
  labs(x = p$speedLabel, y = p$speedMatchLabel)
plotNoOutliers
```

```{r averaging, message=FALSE}
freqMatch <- datFreqMatch %>% 
  group_by(subject, radius, speed, number) %>%
  do(bootstrappinggeom(., x = 'response',  B = p$B, name = 'speedMatch')) 

freqMatch <- freqMatch %>% 
  mutate(freq = speed / (2 * pi * radius), 
         tf = freq * number, 
         freqMatch = speedMatch /  (2 * pi * 3), 
         freqMatchMin = speedMatchMin /  (2 * pi * 3), # radius 3 for the prove
         freqMatchMax = speedMatchMax /  (2 * pi * 3),
         tfMatch = freqMatch * 1, # 1 object for the prove
         tfMatchMin = freqMatchMin * 1, 
         tfMatchMax = freqMatchMax * 1,
         freqMatchDif = freqMatch - freq,
         freqMatchMinDif = freqMatchMin - freq,
         freqMatchMaxDif = freqMatchMax - freq)
```

#### In terms of `r p$speedLabel` 
```{r plotSpeed, message=FALSE}
pFreqMatchSpeedRadius <- ggplot(freqMatch)+
  facet_grid(number ~ subject)+
  geom_abline(slope = 1, lty = 2)+
  geom_pointrange(data = freqMatch, 
                  aes(x = speed, y = speedMatch, ymin = speedMatchMin, 
                      ymax = speedMatchMax, color = factor(radius))) + 
  geom_line(data = freqMatch, aes(x = speed, y = speedMatch, 
                                  color = factor(radius))) +

  scale_x_log10(breaks = 2^(1:5))+scale_y_log10(breaks = 2^(1:5)) +
  labs(x = p$speedLabel, y = p$speedMatchLabel)
pFreqMatchSpeedRadius

pFreqMatchSpeedNumber <- ggplot(freqMatch, 
                 aes(x = speed, y = speedMatch, ymin = speedMatchMin, 
                     ymax = speedMatchMax, color = factor(number)))+
  facet_grid(radius ~ subject)+
  geom_abline(slope = 1, lty = 2)+
  geom_pointrange()+geom_line()+
  scale_colour_manual(values=c(3,4)) +
  scale_x_log10(breaks = 2^(1:5))+scale_y_log10(breaks = 2^(1:5)) +
  labs(x = p$speedLabel, y = p$speedMatchLabel)
pFreqMatchSpeedNumber
```

#### In terms of `r p$freqLabel` 

```{r plotFreq, message=FALSE}
pFreqMatchFreqRadius <- ggplot(freqMatch, 
                 aes(x = freq, y = freqMatch, ymin = freqMatchMin, 
                     ymax = freqMatchMax, color = factor(radius)))+
  facet_grid(number ~ subject)+
  geom_abline(slope = 1, lty = 2)+
  geom_pointrange()+geom_line()+
   scale_x_log10(breaks = c(.125,.25,.5,1,2,4))+
  scale_y_log10(breaks =  c(.125,.25,.5,1,2,4))+
  labs(x = p$freqLabel, y = p$freqMatchLabel)
pFreqMatchFreqRadius

pFreqMatchFreqNumber <- ggplot(freqMatch, 
                 aes(x = freq, y = freqMatch, ymin = freqMatchMin, 
                     ymax = freqMatchMax, color = factor(number)))+
  facet_grid(radius ~ subject)+
  geom_abline(slope = 1, lty = 2)+
  geom_pointrange()+geom_line()+
  scale_colour_manual(values=c(3,4)) +
  scale_x_log10(breaks = c(.125,.25,.5,1,2,4))+
  scale_y_log10(breaks =  c(.125,.25,.5,1,2,4))+
  labs(x = p$freqLabel, y = p$freqMatchLabel)
pFreqMatchFreqNumber
```

#### In terms of `r p$tfLabel` 

```{r plotLocalFreq, message=FALSE}
pFreqMatchTfRadius <- ggplot(freqMatch, 
                 aes(x = tf, y = tfMatch, ymin = tfMatchMin, 
                     ymax = tfMatchMax, color = factor(radius)))+
  facet_grid(number ~ subject)+
  geom_abline(slope = 1, lty = 2)+
  geom_pointrange()+geom_line()+
   scale_x_log10(breaks = c(.125,.25,.5,1,2,4))+
  scale_y_log10(breaks =  c(.125,.25,.5,1,2,4))+
  labs(x = p$tfLabel, y = p$tfMatchLabel)
pFreqMatchTfRadius

pFreqMatchTfNumber <- ggplot(freqMatch, 
                 aes(x = tf, y = tfMatch, ymin = tfMatchMin, 
                     ymax = tfMatchMax, color = factor(number)))+
  facet_grid(radius ~ subject)+
  geom_abline(slope = 1, lty = 2)+
  geom_pointrange()+geom_line()+
  scale_colour_manual(values=c(3,4)) +
  scale_x_log10(breaks = c(.125,.25,.5,1,2,4))+
  scale_y_log10(breaks =  c(.125,.25,.5,1,2,4))+
  labs(x = p$tfLabel, y = p$tfMatchLabel)
pFreqMatchTfNumber
```
Excepting participant FE, who seems to match speed, the rest of the participants matched frequency.

#### Plotting the normalized perceived frequency 
```{r plotFreqDif, message=FALSE}

freqMatchFig<- freqMatch
freqMatchFig$numberFig<- freqMatch$number
freqMatchFig$numberFig <- factor(freqMatchFig$numberFig,
                      levels = c(1, 2),
                      labels = c('1 object', '2 objects'))

freqMatchFig <- freqMatch
freqMatchFig$numberFig <- freqMatchFig$number
freqMatchFig$numberFig <- factor(freqMatchFig$numberFig,
                      levels = c(1, 2),
                      labels = c(p$oneObjectLabel, p$twoObjectsLabel))

freqMatchFig$radiusFig <- freqMatchFig$radius
freqMatchFig$radiusFig <- factor(freqMatchFig$radiusFig,
                      levels = c(2, 4),
                      labels = c(p$smallRadiusLabel, p$largeRadiusLabel))

freqMatchFig$subjectFig <- paste('Observer',freqMatchFig$subject)

pFreqMatchFreqRadiusDif <- ggplot(freqMatchFig, 
                 aes(x = freq, y = freqMatch / freq, 
                     ymin = freqMatchMin / freq, 
                     ymax = freqMatchMax/ freq, 
                     color = factor(radiusFig),
                     shape = factor(radiusFig)))+
  facet_grid(numberFig ~ subjectFig)+
  geom_hline(yintercept = 1, lty = 2,size = p$sizeLine)+
  geom_linerange(size = p$sizeLine, width=.04)+
  geom_point(size = p$sizePointSpeed)+
  geom_line(size = p$sizeLine)+
  scale_y_continuous(breaks=c(1,2),labels=c('1.0','2.0'))+
  scale_x_log10(breaks = p$breaksFreq, labels = p$breaksFreqLabel)+
  labs(x = p$freqLabel, y = p$normalizedDifFreqLabel,  color = p$radiusLabel,
        shape = p$radiusLabel)+
    theme(panel.grid=element_blank(),
        legend.key = element_blank())
pFreqMatchFreqRadiusDif


freqMatchFigNumber <- freqMatchFig
freqMatchFigNumber$freq[freqMatchFigNumber$number==2] <- 
freqMatchFigNumber$freq[freqMatchFigNumber$number==2] * 1.08

freqMatchFigNumber$subjectFig <- paste('Observer',freqMatchFigNumber$subject)

pFreqMatchFreqNumberDif <- ggplot(freqMatchFigNumber, 
                 aes(x = freq, y = freqMatch / freq, 
                     ymin = freqMatchMin / freq, 
                     ymax = freqMatchMax/ freq, 
                     color = factor(numberFig),
                     shape = factor(numberFig)))+
  facet_grid(radiusFig ~ subjectFig)+
  geom_hline(yintercept = 1, lty = 2,size = p$sizeLine)+
  geom_linerange(size = p$sizeLine, width=.04)+
  geom_point(size = p$sizePointSpeed)+
  geom_line(size = p$sizeLine)+
  scale_color_manual(values = c(3,4)) +
  scale_y_continuous(breaks=c(1,2),labels=c('1.0','2.0'))+
  scale_x_log10(breaks = p$breaksFreq, labels = p$breaksFreqLabel)+
  labs(x = p$freqLabel, y = p$normalizedDifFreqLabel,  color = p$numberLabel,
        shape = p$numberLabel)+
    theme(panel.grid=element_blank(),
        legend.key = element_blank())
pFreqMatchFreqNumberDif

```


```{r output}
write.table(freqMatch,'logdata/freqMatch.txt')
```
